---
title: "Spanish Political Parties in twitter"
author: "Guillem Bassa"
date: "19/10/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

```{r}
pacman::p_load(remotes,httpuv, rtweet, tidyverse, stringr, quanteda )

```
For this study we will check the different spanish political parties with representation twitter account's and from them extract the information about the topics that they use the most.
First of all, we need to get the data, so we get the timeline of all the parties.

```{r}
parties_usernames <- c("ciudadanoscs","psoe", "populares","podemos","esquerra_erc", "juntsxcat", "cupnacional", "vox_es", "ehbildubizkaia", "eajpnv_congreso", "maspais_es", "coalicion", "teruelexiste_", "oloque", "prcantabria")

#data_parties <- get_timelines(parties_usernames, n = 3200 )
#save_as_csv(data_parties, "C:/Users/Guillem/Documents/GitHub/spanish-political-parties-topics-in-twitter/database.csv")
data_parties <-read.csv("database.csv", fileEncoding = "UTF-8")
```


```{r}

DATAPROVA <- data_parties
DATAPROVA <- DATAPROVA %>%
  mutate(created_at = as.character(created_at))%>%
  separate(created_at,c("Date","Hour"),  " ", remove = FALSE)
DATAPROVA <- DATAPROVA %>% 
  mutate(Date = as.Date(Date)) %>% 
  filter(Date > "2020-09-19")

```

With the data we can now check for the most used words for every party

First we check the parties who twits the most.

```{r}


ts_plot(dplyr::group_by(DATAPROVA, screen_name), "weeks" )

```

Data cleaning

```{r}
DATAPROVA2 <- DATAPROVA%>%
  group_by(screen_name, is_retweet) %>%
  summarize(n=n())%>%
  mutate(prop=n/sum(n))%>%
  subset(select=c("screen_name","is_retweet","prop"))%>%
  spread(screen_name, prop)  

# 4. Eliminación de ruido - Objetos particulares de Twitter que no son texto 
DATAPROVA$ctext <- gsub("\\@[A-z0-9_\\.]+", "", DATAPROVA$text) # usuarios
DATAPROVA$ctext <- gsub("#[A-z0-9_\\.]+", "", DATAPROVA$ctext) # Hashtags
DATAPROVA$ctext <- gsub(" ?(f|ht)(tp)(s?)(://)(.*)[.|/](.*)", "", DATAPROVA$ctext) # urls
DATAPROVA$ctext <- gsub("\\d", "", DATAPROVA$ctext)


der <- corpus(DATAPROVA$ctext)
docvars(der, "id") <- DATAPROVA$status_id
docvars(der, "Usuario") <- DATAPROVA$screen_name
docvars(der, "Retweet") <- DATAPROVA$is_retweet

toks <- tokens(der, what = "word",
               remove_url = T,
               remove_numbers = T, 
               remove_punct = T,
               remove_symbols = T, 
               remove_separators = T,
               verbose = quanteda_options("verbose"), 
               include_docvars = TRUE)

#minimum 3 characters
toks <- tokens_remove(toks, min_nchar=4)


```

```{r}

#not include the spanish words that doesn't have meaning

toks <- tokens_remove(toks, stopwords ("spanish"))
toks <- tokens_remove(toks, stopwords("ca", source = "stopwords-iso"))

dfm <- dfm(toks)

dfm.df <- convert(dfm[1:10000,1:10000], to="data.frame")


```

```{r}
freq <- textstat_frequency(dfm, n = 5, groups = docvars(dfm, 'Usuario'))

library(RColorBrewer)
colors = c("red", "blue", "darkgreen", "brown", "orange", "pink", "blue", "cyan", "yellow", "black", "purple", "gray", "chartreuse","aquamarine")


dfm %>% 
  textstat_frequency(n = 4, groups = docvars(dfm, 'Usuario')) %>% 
  ggplot(aes(x = reorder(feature, frequency), y = frequency, color=group)) +
  geom_point() +
  coord_flip() +
  labs(x = NULL, y = "Frequency") +
  theme_minimal()+
  scale_color_manual(values = colors)
  
```

# The 100 most used words 
Sum of all parties' tweets

```{r}
textplot_wordcloud(dfm, max_words = 100)
```

```{r}
# 1.2. Términos en contexto
#  ¿Cómo se usan palabras clave en su contexto?
ind.kw <- kwic(toks, 'gobierno')

#100 mes usades CANVIAR 
textplot_xray(ind.kw)
```


```{r}

# Seleccionar los términos más frecuentes
feat <- names(topfeatures(fcm, 50))
fcm <- fcm_select(fcm, feat)
dim(fcm)
head(fcm)

# Red de co-occurrencia - redes semánticas
size <- log(colSums(dfm_select(dfm, feat)))
textplot_network(fcm, min_freq = 0.8, vertex_size = size / max(size) * 3)

# 1.4. Similitud - cercanía entre términos
tsim <- textstat_simil(dfm, dfm[, c("covid", "pandemia", "crisis")], method = "cosine",
                       margin = "features")
head(as.matrix(tsim), 10)

as.list(tsim, n = 6)


```




colors = c("red", "blue", "white", "brown", "orange", "pink", "blue", "cyan", "yellow", "black", "purple", "gray", "chartreuse","bisque","aquamarine")
