---
title: "Spanish Political Parties in twitter"
author: "Guillem Bassa"
date: "19/10/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

```{r}
pacman::p_load(remotes,httpuv, rtweet, tidyverse )

```
For this study we will check the different spanish political parties with representation twitter account's and from them extract the information about the topics that they use the most.
First of all, we need to get the data, so we get the timeline of all the parties.

```{r}
parties_usernames <- c("ciudadanoscs","psoe", "populares","podemos","esquerra_erc", "juntsxcat", "cupnacional", "vox_es", "ehbildubizkaia", "eajpnv_congreso", "maspais_es", "coalicion", "teruelexiste_", "oloque", "prcantabria")

#data_parties <- get_timelines(parties_usernames, n = 3200 )
#save_as_csv(data_parties, "C:/Users/Guillem/Documents/GitHub/spanish-political-parties-topics-in-twitter/database.csv")
data_parties <-read.csv("database.csv", fileEncoding = "UTF-8")
```


```{r}
library(stringr)

DATAPROVA <- data_parties
DATAPROVA <- DATAPROVA %>%
  mutate(created_at = as.character(created_at))%>%
  separate(created_at,c("Date","Hour"),  " ", remove = FALSE)
DATAPROVA <- DATAPROVA %>% 
  mutate(Date = as.Date(Date)) %>% 
  filter(Date > "2020-09-19")

```

With the data we can now check for the most used words for every party

```{r}
pacman::p_load(quanteda)

#see who twits the most by weeks

ts_plot(dplyr::group_by(DATAPROVA, screen_name), "weeks" )

```
```{r}
DATAPROVA2 <- DATAPROVA%>%
  group_by(screen_name, is_retweet) %>%
  summarize(n=n())%>%
  mutate(prop=n/sum(n))%>%
  subset(select=c("screen_name","is_retweet","prop"))%>%
  spread(screen_name, prop)  

# 4. Eliminación de ruido - Objetos particulares de Twitter que no son texto 
DATAPROVA$ctext <- gsub("\\@[a-zA-Z0-9_\\.]+", "", DATAPROVA$text) # usuarios
DATAPROVA$ctext <- gsub("#[a-zA-Z0-9_\\.]+", "", DATAPROVA$ctext) # Hashtags
DATAPROVA$ctext <- gsub(" ?(f|ht)(tp)(s?)(://)(.*)[.|/](.*)", "", DATAPROVA$ctext) # urls


der <- corpus(DATAPROVA$ctext)
docvars(der, "id") <- DATAPROVA$status_id
docvars(der, "Usuario") <- DATAPROVA$screen_name
docvars(der, "Retweet") <- DATAPROVA$is_retweet

toks <- tokens(der, what = "word",
               remove_url = T,
               remove_numbers = T, 
               remove_punct = T,
               remove_symbols = T, 
               remove_separators = T,
               verbose = quanteda_options("verbose"), 
               include_docvars = TRUE)

#minimum 3 characters
toks <- tokens_remove(toks, min_nchar=3)

head(toks)

```

colors = c("red", "blue", "white", "brown", "orange", "pink", "blue", "cyan", "yellow", "black", "purple", "gray", "chartreuse","bisque","aquamarine")
